PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added diagnostic chunk eating disorder with binge eating vs without binge eating, however anorexia can also be with binge eating

```{r Check eating_disorders}
glad.mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

>>>>

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r glad mhd restricting_vs_binge_eating_eating_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
                mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders =
      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Anorexia nervosa",
                    "2" = "Eating disorder with binge eating",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(restricting_vs_binge_eating_eating_disorders,
       cumul = F)
```

```{r Check eating_disorders}
glad.mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```
